Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-09 draft/accordionComplexSurfaces.tex
Added a picture.
More pictures and a geometric proof.

\begin{proof}
Let~$c=\alpha_1\cdots\alpha_r$ be an oriented cycle in some walk~$\omega$.
Assume that~$\omega$ is not of form~$\sigma c^\infty$ or~$c^\infty\sigma$.
Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
Since~$\bar Q$ is locally gentle, this substring is~$\beta^{-1} c^l \alpha_1\cdots\alpha_j\gamma^{-1}$.
Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.
\vincent{Should we also give here a geometric argument?}
\end{proof}

@@

\pierreguy{Pic No 7 here.}
Two situations occur.

@@

Thus~$F$ contains a curve going to the puncture.
\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
\pierreguy{Done; I will need two pictures, please, Vincent.}

>>>>

\begin{proof}
Let~$c=\alpha_1\cdots\alpha_r$ be an oriented cycle in some walk~$\omega$.
Assume that~$\omega$ is not of form~$\sigma c^\infty$ or~$c^\infty\sigma$.
Then, up to cyclic reordering of the arrows in~$c$, it contains a substring of the form~$\beta^\pm c^l \alpha_1\cdots\alpha_j\gamma^\pm$, for some arrows~$\beta,\gamma$ not in~$c$, some~$l\geq 1$, and some~$j<r$.
Since~$\bar Q$ is locally gentle, this substring is~$\beta^{-1} c^l \alpha_1\cdots\alpha_j\gamma^{-1}$.
Hence, the walk~$\omega$ contains the two substrings~$\beta^{-1}\alpha_1\cdots\alpha_j\alpha_{j+1}$ and~$\alpha_r\alpha_1\cdots\alpha_j\gamma^{-1}$, and thus self-kisses.

\para{Geometric proof}
An oriented cycle~$c$ corresponds to a puncture in~$\dissection_{\bar Q}$.
Let~$\gamma = \curveof(\omega)$.  The fact that~$\omega$ contains~$c$ translates to the fact that~$\gamma$ makes a full circle around the correponding puncture.
\pierreguy{Pic No 8 here.}

\includegraphics{pgFigNo8.pdf}

Once this cycle is completed, since~$\gamma$ cannot cross itself, it has to continue cycling infinitely around the puncture.  This proves the claim.
\vincent{Should we also give here a geometric argument?}
\end{proof}

@@

\includegraphics{pgFigNo7.pdf}
\pierreguy{Pic No 7 here.}
Two situations occur.

@@

Thus~$F$ contains a curve going to the puncture.
\vincent{Should we also give here a geometric argument? Pierre-Guy, could you add that?}
\pierreguy{Done; I will need a picture, please, Vincent.}
